The Chemistry Development Kit (CDK) v2.0: atom typing, depiction, molecular formulas, and substructure searching

### 2017-03-26 article.tex
Added more info about available documentation
Added information about automatic building and testing

The quality of the JavaDocs was originally tested with DocCheck, and
later replaced by a custom written tool called OpenJavaDocCheck. With the move
to Maven (explained later), which does not have integration for this tool,
we adopted CheckStyle (\url{http://checkstyle.sourceforge.net/}). This tool
reports on missing documentation and on documentation which is not properly
annotated in the Java source files.

@@

>>>>

The quality of the JavaDocs was originally tested with DocCheck, and
later replaced by a custom written tool called OpenJavaDocCheck. With the move
to Maven (explained later), which does not have integration for this tool,
we adopted CheckStyle (\url{http://checkstyle.sourceforge.net/}). This tool
reports on missing documentation and on documentation which is not properly
annotated in the Java source files. The new website lists a few resources to
help starting CDK users, including a book~\cite{GroovyCDK} and the
Chemistry Toolkit Rosetta Wiki (\url{http://ctr.wikia.com/wiki/Chemistry_Toolkit_Rosetta_Wiki}).

@@

\subsubsection*{Continuous integration}

The CDK has had an automated build system for many years now. Originally,
Nightly integrated various tools (building, testing, JavaDoc, etc)~\cite{Guha2006}.
After the move to Maven, running various steps could be done with Maven,
and Jenkins was used to execute the steps (one instance is still running
at \url{https://jenkins.bigcat.unimaas.nl/job/cdk/}. The online Travis-CI
service is used to build all branches, including pull requests, to ensure
everything properly compiles: \url{https://travis-ci.org/cdk/cdk}.
